### 2019-08-19 maciek.tex
Lower bound, simplifications

The OPT places these three components in clusters $A, B and D$, paying $2$ for migrating $a_3$ and $b_3$. The OPT chooses the cluster $D$ so that it does not contain neither $x$, $y$ nor $z$. The configuration of OPT's clusters is then: $A$ contains $a_1, a_2,d_1$, $B$ contains $b_1, b_2,d_2$ and $D$ contains $a_3, b_3, d_3$.

The next action of the adversary depends on the choice of $x, y, z$.
If $x$ and $y$ have different color (i.e., initially they belong to different clusters), then we issue a request between $x$ and any other node with the same color as $x$. As $x$ do not intersect with $D$, the OPT has them co-located in one server, and it pays no cost for such requests. We issue such requests until $x$ and $y$ have the same color.

Then, we issue a request $(x, y)$.

>>>>

The OPT places these three components in clusters $A, B and D$, paying $2$ for migrating $a_3$ and $b_3$. The OPT has the freedom of choice of the cluster $D$ depending on the choices of the algorithm. We choose $D$ in such way that it does not contain neither $x$ nor $y$, and furthermore that the algorithm places any of nodes from $D$ at $x$ or $y$'s place as the last possible move.
The configuration of OPT's clusters is then: $A$ contains $a_1, a_2,d_1$, $B$ contains $b_1, b_2,d_2$ and $D$ contains $a_3, b_3, d_3$.

From this point, OPT does not change its configuration, and the adversary continues to issue a request between $x$ and any other node with the same color as $x$.
Upon receiving this request, ALG pays for it the cost $1$ and it increases its number of clusters that contain non-singleton components.
This procedure ends when ALG has no more clusters with singleton-only components left or ALG manages to put $d_1, d_2$ or $d_3$ in place of $x$ or $y$.

At the begining, ALG has $\ell$ singleton-only components and each request increases their number by $1$.
Furthermore, before reaching either $d_1, d_2$ or $d_3$ in place of $x$ or $y$, the algorithm must cycle through $\Omega(\ell)$ nodes from other clusters. This is guaranteed as the choice of $D$ can depend on the actions of the deterministic algorithm.
In total, OPT pays $2$, and ALG pays $\Omega(\ell)$.

%The next action of the adversary depends on the choice of $x, y, z$.
%If $x$ and $y$ have different color (i.e., initially they belong to different clusters), then we issue a request between $x$ and any other node with the same color as $x$. As $x$ do not intersect with $D$, the OPT has them co-located in one server, and it pays no cost for such requests. We issue such requests until $x$ and $y$ have the same color.

%Note that the adversary can foresee the actions of the algorithm, and may choose $D$ in such way, that $x$ cycles through all other clusters before reaching $D$, paying the cost of $\Omega(k)$, which would already suffice to show the lower bound.

%Then, $x$ and $y$ have the same color, and we issue a request $(x, y)$. As these have the same color (and there are different than $d_1, d_2$ and $d_3$), OPT pays no cost for this request, and ALG pays $2$ for migrating $x$ and $y$ to other cluster.
%We repeat the entire process, i.e., we force ALG to choose $x$ and $y$ of the same color, and issue such request that is free for OPT. This process can continue until ALG has no more clusters with singleton components, or it pays the cost $\Omega(k)$ already.
